

---
Batting Statistics Visualization
===

In this document, I will explain the steps taken to create a graphical visualization of batting statistics from 2010-2015.


###Graph 1

The first graph is a visualization of all the all star players from 2010. This graph compares their hits and at bats for the season. There is a large discrepancy in the graph between the worst batters and best batters. This is due to the pitchers being poor batters compared to other positions.

```{r}
source("../02 Data Wrangling/batting + allstar.R", echo = TRUE)
```



###Graph 2

The second graph is a visualization of all professional players and their salaries from 2010. The data is distinguished by whether they made the all-star game (colored key by position: 10 (pitcher), 2 (catcher), 3 (first baseman), 4 (second baseman), 5 (third baseman), 6 (shortstop), 7 (left fielder), 8 (center fielder), and 9 (right fielder)) or not(gray points). This visualization shows how salary is affected by position.

```{r}
source("../02 Data Wrangling/salary + allstar.R", echo = TRUE)
```


###Graph 3

This graph compares the best offensive and defensive catchers in 2010. The x-axis corresponds to runners the cather has thrown out trying to steal. While the y-axis shows HR. This graph shows which catchers excel offensively, defensively and boths

```{r}
source("../02 Data Wrangling/salary + batting.R", echo = TRUE)
```
